Topic 21 Experiment and analysis

### 2018-05-11 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
Update to TeX file for meeting and figures

\begin{frame}{Current scan at constant B$_t$ in L-Mode plasma}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsNe5IpConstantBt}
      \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
      \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
      \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
      \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
      \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
      \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan done for each of
          the machine
        \item<1|only@1> The scan implies a modification of the
          L$_{\parallel}$. There is a factor of 5 difference between
          the two machines due to the very long outer divertor leg of TCV
        \item<2|only@2> AUG: Fueling reduced only at lower I$_p$ to
          avoid earlier disruption. Similar neutral pressure in the
          subdivertor region reached. NBI additional power added to
          keep power in the SOL approximately constant
        \item<3|only@3> TCV: Ohmic heating only. Similar neutral compression reached and
          D$_{\alpha}$ radiation from the floor. Ion flux rollover
          reached in all the three current,  although marginally at
          330 kA
        \item<4|only@4> Divertor neutral density estimated starting
          from D$_{\alpha}$ calibrated camera and using electron
          density and temperature from LP data. Neutral density
          increases earlier in edge density at lower current
        \item<5|only@5> Neutrals behavior reconciled whenever
          comparison considered as a function of Greenwald fraction  
        \item<6|only@6> For both AUG and TCV flattening of normalized
          upstream profile reached \alert{earlier in density at lower
            current.} For both the machine the increase of $\lambda_n$
          reached for larger values of $\Lambda_{div}$
        \item<7|only@7> Quantifying profile evolution using the
          \alert{shoulder amplitude metric} introduce by Wynn and
          Lipschultz for JET. \alert{Amplitude is the difference
            between normalized upstream density profiles}
        \only<8-9>{\item Amplitude evolve faster in density at lower
          current in the far SOL \onslide<9>{\alert{but once evolution \textit{vs} greenwald
            fraction is considered the evolution is equivalent between
            different current}}}
        \item<10|only@10> Amplitude evolution still reconciled in AUG if
          considered as a function of local evolution of $\Lambda_{div}$
        \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
          with blob size without significant difference within the
          current explored
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

>>>>

\begin{frame}{Current scan at constant B$_t$ in L-Mode plasma}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
      \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantBt}
      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsGreenwaldConstantBt}
      \only<6>{
        \begin{tikzonimage}[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantBt}
          \draw [thick, ta3orange, ->] (0.27, 0.9) -- (0.27, 0.8);
          \draw [thick, ta3orange, ->] (0.77, 0.45) -- (0.77, 0.55);
        \end{tikzonimage}
      }
      \includegraphics<7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantBt}
      % \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
      % \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
      % \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
      % \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
      % \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan done for each of
          the machine
        \item<1|only@1> The scan implies a modification of the
          L$_{\parallel}$. There is a factor of 5 difference between
          the two machines due to the very long outer divertor leg of TCV
        \item<2|only@2> AUG: Fueling reduced only at lower I$_p$ to
          avoid earlier disruption. Similar neutral pressure in the
          subdivertor region reached. NBI additional power added to
          keep power in the SOL approximately constant
        \item<3|only@3> TCV: Ohmic heating only. Similar neutral compression reached and
          D$_{\alpha}$ radiation from the floor. Ion flux rollover
          reached in all the three current,  although marginally at
          330 kA
        \item<4|only@4> In both the machines both the peak target
          density and the radiation close to divertor target exhibit
          rollover at increasing density with increasing current
        \item<5|only@5> Whenever considered as a a function of
          Greenwald fraction the behaviors at different currents
          almost reconciled for AUG \alert{but not for TCV}
        \item<6|only@6> We now consider the Target and upstream
          profiles at the same level of densities
        \item<7|only@7> For both AUG and TCV flattening of normalized
          upstream profile reached \alert{earlier in density at lower
            current.} For both the machine the increase of $\lambda_n$
          reached for larger values of $\Lambda_{div}$
        % \item<7|only@7> Quantifying profile evolution using the
        %   \alert{shoulder amplitude metric} introduce by Wynn and
        %   Lipschultz for JET. \alert{Amplitude is the difference
        %     between normalized upstream density profiles}
        % \only<8-9>{\item Amplitude evolve faster in density at lower
        %   current in the far SOL \onslide<9>{\alert{but once evolution \textit{vs} greenwald
        %     fraction is considered the evolution is equivalent between
        %     different current}}}
        % \item<10|only@10> Amplitude evolution still reconciled in AUG if
        %   considered as a function of local evolution of $\Lambda_{div}$
        % \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
        %   with blob size without significant difference within the
        %   current explored
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}
